---
title: "COVID19 patients in ICU in Sweden"
output:
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
always_allow_html: yes
---


```{r message=TRUE, warning=TRUE, include=FALSE}
knitr::opts_chunk$set(message=TRUE, warning=TRUE, eval=TRUE)
library(readxl)
library(dplyr)
library(readr)
library(ggplot2)
library(tidyr)
library(knitr)
library(kableExtra)
library(patchwork)

theme_basic <- theme_bw() +theme(panel.border = element_blank(), axis.line = element_line(colour = 'black'))

theme_biggerfonts <- theme(
  axis.title.x=element_text(size=14), 
  axis.title.y=element_text(size=14,angle=90, margin = margin(t = 0, r = 5, b = 0, l = 15)), 
  axis.text.x=element_text(size=12), 
  axis.text.y=element_text(size=12), 
  strip.text.x=element_text(size=14), 
  legend.text=element_text(size=12), 
  legend.title=element_text(size=14))

theme_set(theme_basic + theme_biggerfonts)


summarise_missing <- function(df,varnames) {
  df %>% 
    ungroup() %>% 
    summarise_at(vars(varnames),
               list(missing.n = ~sum(is.na(.)),
                    missing.pct = ~100*sum(is.na(.))/n())) 
  }

summarise_qvars <- function(df,varnames) {
  df %>% 
    summarise_at(vars(varnames),
                      list(median = ~median(., na.rm = TRUE),
                           Q1 = ~quantile(., 1/4, na.rm = TRUE),
                           Q3 = ~quantile(., 3/4, na.rm = TRUE),
                           min = ~min(., na.rm = TRUE),
                           max = ~max(., na.rm = TRUE),
                           n = ~sum(!is.na(.)),
                           missing.n = ~sum(is.na(.)),
                    missing.pct = ~100*sum(is.na(.))/n()
                           )) %>% 
  kable() %>% kable_styling(full_width = F)
}

summarise_dvar <- function(df,varname) {
  df %>% 
    ungroup() %>% 
    mutate(N = sum(!is.na({{varname}}))) %>% 
    group_by({{varname}}) %>% 
  summarise(n = n(), 
            Percent = 100*n()/N[1]) %>% 
  kable() %>% kable_styling(full_width = F)
}

```

# Read in the data
## N unique IDs
```{r echo=FALSE, message=FALSE, warning=FALSE}
datafile <- 'Raw data/MichelleChew_SweCOVID ICU Study_Unique_pjb_23jun_N809x_recoded_npwd.xlsx'
basicdata <- read_excel(datafile, na='NULL', sheet = 'Basic data') %>% 
  mutate(Height = parse_number(Height),
         ArrivalWeight = parse_number(ArrivalWeight)) 

basicdata %>% 
  summarise(nRows = n(), nIDs = n_distinct(PersonalID)) %>% 
  kable() %>% kable_styling(full_width = F)

totalN <- nrow(basicdata)

diagnosisdata <- read_excel(datafile, na='NULL', sheet = 'AllDiagnoses', range = 'A1:UB1609')

SOFAdata <- read_excel(datafile, na='NULL', sheet = 'SOFA', range = 'A1:BX1609')

measuresdata <- read_excel(datafile, na='NULL', sheet = 'Measures', range = 'A1:BC1609')

SIRIdata <- read_excel(datafile, na='NULL', sheet = 'SIRI', range = 'A1:AZ1609')

```

# Zoom call variables
These are things that I couldn't identify in "Statistical analysis plan for "SweCOVID ICU study.docx" but I had made a note to do it in our zoom call

## Height
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  summarise_missing('Height') %>% 
  kable() %>% kable_styling(full_width = F)

basicdata %>% 
  group_by(Gender) %>% 
  summarise_qvars(c('Height'))

basicdata %>% 
  ggplot(aes(x = Height, fill = Gender)) +
  geom_histogram(binwidth = 0.05, alpha = 0.7) +
  labs(x = 'Height (metres)')
```

## Arrival Weight
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  summarise_missing('ArrivalWeight') %>% 
  kable() %>% kable_styling(full_width = F)

basicdata %>% 
  group_by(Gender) %>% 
  summarise_qvars(c('ArrivalWeight'))

basicdata %>% 
  ggplot(aes(x = ArrivalWeight, fill = Gender)) +
  geom_histogram(binwidth = 5, alpha = 0.7) +
  labs(x = 'Arrival Weight (kilograms')
```

# Ventilation

DG021 invasive mechanical ventilation 

```{r echo=FALSE, message=FALSE, warning=FALSE}

```

DG023 noninvasive mechanical ventilation *descriptive only

DG028 ? * descriptive only 

DR020 dialysis * multiv. analysis 

- these are not mutually exclusive

## Medication
are these variables different? OtherMedicineCovid CovidMedicineOther

### Specific pharmacotherapy
any yes in CovidMedicineKlorokinfosfat	CovidMedicineTocilizumab	CovidMedicineLopinavirRitonavir	CovidMedicineDarunavir	CovidMedicineLopinavir	CovidMedicineRemdesivir	CovidMedicineBaricitinib	CovidMedeicineSteroids

### Chloroquine
CovidMedicineKlorokinfosfat

### Tocilizumab
CovidMedicineTocilizumab

### Lopinavir/Ritonavir
any yes in CovidMedicineLopinavirRitonavir	or CovidMedicineLopinavir

### Remsedivir 
CovidMedicineRemdesivir

CovidMedicineBaricitinib	

### Steroids
CovidMedeicineSteroids

### Other
any yes in CovidMedicineDarunavir CovidMedicineVitamineC CovidMedicineOther

# Word doc variables
The headings below are from the list in "Statistical analysis plan for "SweCOVID ICU study.docx" with some additional stuff - read comments for details

## Age
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  summarise_missing('Age') %>% 
  kable() %>% kable_styling(full_width = F)
```

### Age Group
Categorized data <50 years, 50-59 years, 60-69 years, 70-79 years and >80 years of age

```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  mutate(AgeGroup = case_when(Age < 50 ~ '<50',
                              between(Age,50,59) ~ '50-59',
                              between(Age,60,69) ~ '60-69',
                              between(Age,70,79) ~ '70-79',
                              Age >= 80 ~ '80+',
                              TRUE ~ as.character(NA))
         ) %>% 
  group_by(AgeGroup) %>% 
  summarise(minAge = min(Age), 
            maxAge = max(Age), 
            n = n(),
            Percent = 100*n()/totalN) %>% 
  kable() %>% kable_styling(full_width = F)

```

### Aged over 65
Proportion of patients >65 years of age
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  mutate(AgeOver65 = Age > 65) %>% 
  summarise_dvar(AgeOver65)
  
```
## Sex
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  summarise_missing('Gender') %>% 
  kable() %>% kable_styling(full_width = F)

basicdata %>% 
  summarise_dvar(Gender) 
  
```
## SAPSIII score
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% summarise_qvars(c('SAPS3TotalPoints')) 

basicdata %>% 
  ggplot(aes(x=SAPS3TotalPoints)) +
  geom_histogram(binwidth = 3) 

```

## SOFA score on admission 
sequential organ failure score
```{r echo=FALSE, message=FALSE, warning=FALSE}
SOFAdata %>% 
  summarise_qvars(c('SOFATotalPoint')) 

SOFAdata %>% 
  ggplot(aes(x=SOFATotalPoint)) +
  geom_histogram(binwidth = 1) 

```
### SOFA score separating out the zeros
Note that NAs are filtered out so the 'missing' values are 0. True missing values are reported above.
```{r echo=FALSE, message=FALSE, warning=FALSE}
SOFAdata %>% 
  filter(!is.na(SOFATotalPoint)) %>% 
  mutate(SOFAmore.than.0 = SOFATotalPoint > 0) %>% 
  summarise_dvar(SOFAmore.than.0) 

SOFAdata %>% 
  filter(!is.na(SOFATotalPoint)) %>% 
  filter(SOFATotalPoint > 0) %>% 
  summarise_qvars(c('SOFATotalPoint')) 

SOFAdata %>% 
  filter(SOFATotalPoint > 0) %>% 
  ggplot(aes(x=SOFATotalPoint)) +
  geom_histogram(binwidth = 1) 

```

## Comorbidities (any)
MC: *"Comorbidities: this is highly dependent on how it is defined and SIR has a very broad definition. I think we should list hypertension, chronic heart disease (SIRI X), chronic lung disease (SIRI Y), diabetes (SIRI AD), chronic renal disease (SIRI AC), chronic hepatic disease (SIRI AB), chronic neuromuscular disease (SIRI AF), immunosuppression (SIRI Z). The incidence of ‘any comorbidity’ is any ‘yes’ among any of these."*

Also N comorbidities

```{r echo=FALSE, message=FALSE, warning=FALSE}
comorbiddata <- SIRIdata %>% 
  select(c('PersonalID',
           'RiskHypertension',
           'RiskChronicHeartDisease',
           'RiskChronicLungDisease',
           'RiskDiabetes',
           'RiskChronKidneyDisease',
           'RiskChronicLiverDisease',
           'RiskNeuroMuscDisease',
           'RiskReducedImmuneDefence')) %>% 
      pivot_longer(cols = -c(PersonalID),
                   names_to = c('Comorbidity')) %>% 
      group_by(PersonalID) %>%
      summarise(RiskN = sum(value, na.rm = TRUE),
                RiskAny = sign(sum(value, na.rm = TRUE)
                               ))

comorbiddata %>% 
  group_by(RiskN) %>% 
  summarise_dvar(RiskN) 

comorbiddata %>% 
  group_by(RiskAny) %>% 
  summarise_dvar(RiskAny) 

```	

<span style="color: red;">I had noted these from the zoom conversation, but I suppose they aren't needed? </span>
+ Risk65	
+ RiskChronicHeartLungDisease 
+ RiskReducedImmuneDefence	
+ RiskChronicLiverKidneyDisease	
+ RiskOther

## Hypertension
```{r echo=FALSE, message=FALSE, warning=FALSE}
SIRIdata %>% 
  summarise_dvar(RiskHypertension)

```


## Chronic Heart Disease
```{r echo=FALSE, message=FALSE, warning=FALSE}
SIRIdata %>% 
  summarise_dvar(RiskChronicHeartDisease)

```	

## Chronic Lung Disease
```{r echo=FALSE, message=FALSE, warning=FALSE}
SIRIdata %>% 
  summarise_dvar(RiskChronicLungDisease)
```	
	
## Obesity 

MC: *"SIRI data is not accurate. Could you please merge the SIRI data (AE) with Basic Data ‘Arrival BMI’ (AF) and create a new column= ‘Obesity To Use’. This will be any ‘yes’ in SIRI AE and/or any value =>30 in column AF in Basic data. "*
```{r echo=FALSE, message=FALSE, warning=FALSE}

# basicdata %>% 
#   select(PersonalID, ArrivalBMI) %>% 
#   mutate(BMIover30 = as.numeric(ArrivalBMI > 30) ) %>% 
#   full_join(
#     SIRIdata %>% 
#       select(PersonalID, RiskObesity) 
#   ) %>% 
#   replace(BMIover30, is.na(BMIover30), 0) %>% 
#   replace(is.na(RiskObesity), 0) %>% 
#   mutate(RiskObesityToUse = BMIover30 + RiskObesity)



```

## Diabetes Mellitus
```{r echo=FALSE, message=FALSE, warning=FALSE}
SIRIdata %>% 
  summarise_dvar(RiskDiabetes) 

```

## Chronic Renal Disease
```{r echo=FALSE, message=FALSE, warning=FALSE}
SIRIdata %>% 
  summarise_dvar(RiskChronKidneyDisease) 

```
## Chronic Hepatic Disease
```{r echo=FALSE, message=FALSE, warning=FALSE}
SIRIdata %>% 
  summarise_dvar(RiskChronicLiverDisease) 

```

## Chronic Neuromuscular Disease
```{r echo=FALSE, message=FALSE, warning=FALSE}
SIRIdata %>% 
  summarise_dvar(RiskNeuroMuscDisease) 

```

## Immunosuppression
```{r echo=FALSE, message=FALSE, warning=FALSE}
SIRIdata %>% 
  summarise_dvar(RiskReducedImmuneDefence) 

```

## PaO2/FiO2 on admission

PB: *"Now there is BN that is the lowest value for thrombocytes and BT that is the lowest value for oxygenationindex PaO2/FiO2."*

MC: *"I matched any ‘1´ in this column with the PaO2/FiO2 values in Basic Data BT (‘oxygenation index to use’) as well as SOFA R ‘Oxygenation Index’ and AW ’Oxygenation index min’ . I took the lowest of the values in any of these cells to define the degree of ARDS. Where I was able I replaced J809X with J809A,B or C. I managed to recode 34 patients. I also changed J809X to one of the other J809 codes if any of these cells contained a ‘1’."*

<span style="color: red;">I'm assuming Michelle's updates were applied to the same variable, 'OxygenationIndexToUse</span>'

```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  summarise_qvars('OxygenationIndexToUse') 

basicdata %>% 
  ggplot(aes(x=OxygenationIndexToUse)) +
  geom_histogram() +scale_x_log10() +
  plot_annotation(caption = 'The x axis is on a log scale')

```
## Time in hospital prior to ICU admission

```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  summarise_qvars('SAPS3TimeInHospital') 

```

### separating out the zeros
Note that NAs are filtered out so the 'missing' values are 0. True missing values are reported above.
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  filter(!is.na(SAPS3TimeInHospital)) %>% 
  mutate(TIHmore.than.0 = SAPS3TimeInHospital > 0) %>% 
  summarise_dvar(TIHmore.than.0) 

basicdata %>% 
  filter(!is.na(SAPS3TimeInHospital)) %>% 
  filter(SAPS3TimeInHospital > 0) %>% 
  summarise_qvars(c('SAPS3TimeInHospital')) 


basicdata %>% 
  filter(SAPS3TimeInHospital > 0) %>% 
  ggplot(aes(x=SAPS3TimeInHospital)) +
  geom_histogram(bins = 10) + scale_x_log10() +
  plot_annotation(caption = 'The x axis is on a log scale')


```

## WCC on admission
MC: 'SAPS3LeukocytesMax' 

## Platelets on admission
MC: 'TrombocytesToUse'

## Symptom onset to ICU admission
I converted those that had negative values to NA.
```{r echo=FALSE, message=FALSE, warning=FALSE}
SymptomToICUdata <- SIRIdata %>% 
  mutate(DaysToICUFromIllness = if_else(DaysToICUFromIllness < 0, 
                                        as.numeric(NA), 
                                        DaysToICUFromIllness)) 
SymptomToICUdata %>% 
  summarise_qvars('DaysToICUFromIllness') 

SymptomToICUdata %>% 
  ggplot(aes(x=DaysToICUFromIllness)) +
  geom_histogram(binwidth = 1) 

```

## ICU length of stay
variable 'ICUDays' in 'Basic data'
Patrik: "add length of stay for patients that left the ICU alive?"
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  summarise_missing('ICUDays') %>% 
  kable() %>% kable_styling(full_width = F)

basicdata %>% 
  summarise_qvars('ICUDays') 

basicdata %>% 
  ggplot(aes(x=ICUDays)) +
  geom_histogram(binwidth = 3) 

```

## Discharge destination
MC: *I recoded the ‘Discharge to’ column (Z in basic data). Sorry I sent you a wrong file earlier today. The correct file is attached now. the The median ICU stay was 12 days. I recoded ‘Other hospital’ using a simple rule, based on ICU days, X, and ‘reason for discharge, Y’
If X =<12 AND Y=medical indication or belonging there -> recoded to ‘other ICU’. If X>12 AND Y= medical indication or belonging there -> recoded to ‘unknown’. If Y=’lack of resources’ regardless of X -> recoded to ‘other ICU’. The recoded items are listed in red text. According to my quick counts:
+ ‘Other ICU’=97,  
+ ‘Unknown’ =29, 
+ ‘ not discharged’ = 42, 
+ ‘home’ =2, 
+ ‘ward’=1082
+ ‘dead’ = 356
However these are likely to be be slightly inaccurate since the number of dead should be a bit higher. Could you check this new column Z against column AB ‘Care Result’? ‘Deceased’ in AB should be the same as ‘Deceased’ in Z. So you may pick up a few more that way.*

'DischargedTo'
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>%   
  summarise_missing('DischargedTo')

basicdata %>% 
  summarise_dvar(`DischargedTo`)

```
## Other ICU
transfer to other ICUs

Patrik: * "new column H with Number of ICU transfers and column Y with Reason for ICU transfer, being the first discharge reason. The last discharge reason is in column AA."*

### 'NumberOfICUTransfers'
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>%   
  summarise_missing('NumberOfICUTransfers')

basicdata %>% 
  summarise_dvar(NumberOfICUTransfers)

```
### 'ReasonForICUTransfer (First discharge reason)'
There are some patients that have a discharge reason but 0 transfers recorded. This means they were discharged and not transferred. ('ReasonForICUTransfer (First discharge reason)' and 'DischargeReason (Last discharge reason)' should be the same  in these patients - double check.)

```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>%   
  summarise_missing('ReasonForICUTransfer (First discharge reason)') %>% 
  kable() %>% kable_styling(full_width = F)

basicdata %>%   
  summarise_dvar(`ReasonForICUTransfer (First discharge reason)`)

basicdata %>% 
  group_by(NumberOfICUTransfers) %>% 
  summarise(n = n(), 
            Percent = 100*n()/totalN, 
            missing.reason = sum(is.na(`ReasonForICUTransfer (First discharge reason)`))) %>% 
  kable() %>% kable_styling(full_width = F)

basicdata %>% 
  ggplot(aes(x = NumberOfICUTransfers)) +
  facet_wrap(. ~ `ReasonForICUTransfer (First discharge reason)`, scales = 'free') +
  geom_histogram(binwidth = 1) +
  plot_annotation(caption = 'Note different y-axis scales')
```

## Died
'CareResult', result of ICU care
```{r echo=FALSE, message=FALSE, warning=FALSE}
# DaysOffRegistryAfterAdmission

basicdata %>%   
  summarise_missing('CareResult') %>% 
  kable() %>% kable_styling(full_width = F)

basicdata %>% 
  summarise_dvar(CareResult)
```

## Respiratory failure (ARDS)

J809A	J809B	J809C	J809X

A mild, B moderate, C severe, X not specified

 - not mutually exclusive, I have taken the worst

SAPS3 ventilator use variable 'SAPS3Ventilator'

<span style="color: red;">Using the other variable now, right? </span>
```{r echo=FALSE, message=FALSE, warning=FALSE}

respfailvars <- c('J809A',	'J809B',	'J809C',	'J809X')
diagnosisdata %>% 
  summarise_missing(respfailvars) %>% 
  pivot_longer(cols = everything(), 
               names_to = c('variable','.value'),  
               names_sep = '_') %>% 
  kable() %>% kable_styling(full_width = F)

diagnosisdata %>% 
  select(all_of(respfailvars)) %>% 
  mutate(J809worst = case_when(J809X == 1 ~ 'unspecified',
                               J809A == 1 ~ 'mild',
                               J809B == 1 ~ 'moderate',
                               J809C == 1 ~ 'severe',
                               J809X+J809A+J809B+J809C == 0 ~ 'none') %>% 
           factor(levels = c('severe', 'moderate','mild','unspecified','none'))) %>% 
  summarise_dvar(J809worst)

```


## AKI
Renal failure 

MC: *"The incidence of AKI according to KDIGO as calculated by Patrik was 46.3%. It is difficult to say if this is a true representation of its incidence since data was only available for 661 patients. Interestingly the frequency of KDIGO 3 was 17.4% (of 661 patients, column BX in SOFA) which fits in well with the 17.1% found in the ‘MeasuresText’ worksheet, which covers all 1608 patients." - yes, my estimate is different because I tried to extrapolate the missing data from the N17x variables. *

Mc: *"Renal failure: is defined as any of N17x. Patrik has merged this with daily Creatinine values in SOFA, and entered this as a separate column BX in SOFA. I just too the data from here. You lost me on you calculation of estimated AKI!!! Sorry, bit slow. Are you happy to accept Patrik’s manual calculations?"* - I'm happy to do whatever you like, let's discuss.

+NV N179 acute renal failure unspecified
+NU N178 other acute renal failure
+NT N170 acute renal failure with tubular necrosis  

KDIGO minimum
<span style="color: red;">Something got messed up in an update to the data file, this code gives an error now. </span>
```{r echo=FALSE, message=FALSE, warning=FALSE}
renalfailuredata <- diagnosisdata %>% 
  select(c('PersonalID','N179', 'N178', 'N170')) %>% 
  full_join(SOFAdata %>% 
              select(c('PersonalID','KDIGOMin')), 
            by = 'PersonalID') %>% 
  mutate(AnyN17x = N179 + N178 + N170 > 0,
         AnyKDIGOMin = KDIGOMin >0)

renalfailuredata %>% 
  summarise_dvar(AnyN17x)

renalfailuredata %>% 
  summarise_missing(c('AnyN17x','AnyKDIGOMin')) %>% 
  pivot_longer(cols = everything(), 
               names_to = c('variable','.value'),  
               names_sep = '_') %>% 
  kable() %>% kable_styling(full_width = F)

```

yes in any of these N17x? 

BX KDIGO_min more than 0?

Compare these:
```{r echo=FALSE, message=FALSE, warning=FALSE}

xtabs( ~ AnyN17x + AnyKDIGOMin, data = renalfailuredata, addNA = TRUE) 

# renalfailuredata %>% 
#   filter(!is.na(AnyKDIGOMin)) %>% 
#   mutate(N = n()) %>% 
#   group_by(AnyKDIGOMin) %>% 
#     summarise(n = n(), 
#             Percent = 100*n()/N[1])
# 
# renalfailuredata %>% 
#   filter(!is.na(AnyN17x)) %>% 
#   mutate(N = n()) %>% 
#   group_by(AnyN17x) %>% 
#     summarise(n = n(), 
#             Percent = 100*n()/N[1])
```
Fill in missing KDIGO values, using less reliable N17x values as a predictor, based on the rate of agreement where we have both variables. Of 819 KDIGO NAs where AnyN17x was false, we should have 
`r missrate <- 186/(297+186); round(819*missrate)` with a diagnosis.Of 173 KDIGO NAs where AnyN17x was true, we should have `r hitrate <- 99/(34+99); round(99*hitrate)` with a diagnosis.

### New estimated rate of any kind of renal failure (conservative)
```{r echo=FALSE, message=FALSE, warning=FALSE}
tibble(
  n = 186+99+315+74,
  Percent = 100*n/totalN) %>% 
  kable() %>% kable_styling(full_width = F)
```

## ICU mortality
MC says: 'CareResult'
<span style="color: red;">Same variable as 'Died' heading. Redundant?</span>

```{r echo=FALSE, message=FALSE, warning=FALSE}

# basicdata <- basicdata %>% 
#   mutate(DiedNDaysAfterAdmission = case_when(Deceased == 'Yes' ~ DaysOffRegistryAfterAdmission,
#                                              TRUE ~ as.numeric(NA)))
#   
# basicdata %>%   
#   summarise_missing('DiedNDaysAfterAdmission') %>% 
#   kable() %>% kable_styling(full_width = F)
# 
# basicdata %>% 
#   summarise_qvars('DiedNDaysAfterAdmission') 

```

## 30-day mortality
The number of patients that died within 30 days of ICU admission.
'Deceased'
<span style="color: red;">Not sure this is the right variable? But I think you calculated it separately anyway.</span>
```{r echo=FALSE, message=FALSE, warning=FALSE}
basicdata %>% 
  summarise_dvar(Deceased)
  summarise_qvars(c('Deceased'))

```

## % patients with full 30day follow up
<span style="color: red;">What does this depend on? </span>


## % patients still in ICU at 30 day follow up

