---
title: "SweCovICU data management"
author: "Sarah McIntyre"
date: "December 2020"
output:
  html_document:
    df_print: paged
  html_notebook: default
---

# load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(summarytools)
library(janitor)
library(knitr)
library(kableExtra)

datafile <- '../Raw data/SweCOVID_ICU_201207_nopwd.xlsx'

```

# read in the data

## basic data - select and calculate variables
```{r}

basicdata <- 
  read_excel(datafile, na='NULL', sheet = 'Basic data') %>%
  # select variables
  select(c(PersonalID,
           Deceased,
           Age,
           Gender,
           SAPS3TotalPoints,
           ArrivalBMI,
           OxygenationIndexToUse,
           NumberOfICUTransfers,
           SAPS3TimeInHospital, 
           ICUDays,
           AdmissionTime,
           StartIMV,
           IMVonAdm,
           DischargedTo,
           CareResult,
           OffRegistryDate,
           AdmissionRegistration,
           # rename:
           DaysDischargeOffReg = `DaysFromDischargeToOff-registry/Diseased`)) %>%
  # calculate new variables
  mutate(
    # age
    Age65plus = Age >= 65,
    AgeGroup = case_when(Age < 50 ~ '<50',
                        between(Age,50,59) ~ '50-59',
                        between(Age,60,69) ~ '60-69',
                        between(Age,70,79) ~ '70-79',
                        Age >= 80 ~ '80+',
                        TRUE ~ as.character(NA)),
   # BMI / obesity
   BMI40plus = as.numeric(ArrivalBMI >= 40),
   BMIcategory = case_when(ArrivalBMI < 18.5 ~ 'underweight',
                           ArrivalBMI >= 18.5 & ArrivalBMI < 25 ~ 'normal',
                           ArrivalBMI >= 25 & ArrivalBMI < 30 ~ 'overweight',
                           ArrivalBMI >= 30 & ArrivalBMI < 35 ~ 'obesity class 1',
                           ArrivalBMI >= 35 & ArrivalBMI < 40 ~ 'obesity class 2',
                           ArrivalBMI >= 40 ~ 'obesity class 3',
                           ),
   nICUTransfers = if_else(NumberOfICUTransfers >= 3,
                                '3+', as.character(NumberOfICUTransfers)),
   ICUtransferred = NumberOfICUTransfers > 0,
   OxygenationIndex = OxygenationIndexToUse*7.50062, # kPa -> mmHg
   TIHmore.than.0 = SAPS3TimeInHospital > 0,
   SAPS3TimeInHospitalNo0 = if_else(SAPS3TimeInHospital > 0,
                                    SAPS3TimeInHospital, as.numeric(NA)),
            
   # 30 day mortality and days to death
   DaysDischargeOffReg = DaysDischargeOffReg %>% parse_number(),
   # problem triggered: argument "x" is missing, with no default
   # but it still works so warning safe to ignore
   DaysDischargeOffReg = if_else(DaysDischargeOffReg < 0,
                                 as.numeric(NA), DaysDischargeOffReg),
   Mortality30days = recode(Deceased, Yes = TRUE, No = FALSE),
   
   # IMV time
   TimeToIMV = difftime(StartIMV, AdmissionTime, units = 'hours'),
   IMVonAdmission = TimeToIMV <= 24,
   DaysToDeath = 
     as.Date(OffRegistryDate) - as.Date(AdmissionRegistration) - (DaysDischargeOffReg),
         
   #6 march-5april vs 6 April-6May
   AdmissionPeriod = case_when(
     as.Date(AdmissionRegistration) >= "2020-03-06" &
       as.Date(AdmissionRegistration) <= "2020-04-05" ~ '6Mar-5Apr',
     as.Date(AdmissionRegistration) >= "2020-04-06" &
       as.Date(AdmissionRegistration) <= "2020-05-06" ~ '6Apr-6May',
     TRUE ~ as.Date(AdmissionRegistration) %>% as.character() )
  ) %>% 
  select(-c(OxygenationIndexToUse,
            AdmissionTime,
            StartIMV,
            IMVonAdm))

# basicdata %>%
#   group_by(IMVonAdm) %>% tally()
# 
# basicdata %>%
#   group_by(is.na(TimeToIMV)) %>% tally()
# 
# basicdata %>%
#   group_by(IMVonAdmission) %>% tally()

```

## diagnosis sheet - select and calculate variables
```{r}

diagnosisdata <- 
  read_excel(datafile, na='NULL', sheet = 'AllDiagnoses', range = 'A1:TY1609') %>% 
   select(c(PersonalID,
           J809A,
           J809B,
           J809C,
           J809X)) %>%
  mutate(J809worst = case_when(J809C == 1 ~ 'severe',
                       J809B == 1 ~ 'moderate',
                       J809A == 1 ~ 'mild',
                       (J809X+J809A+J809B+J809C) == 0 ~ 'none',
                       J809X == 1 ~ as.character(NA)
                       ))

```


## SOFA sheet - select and calculate variables
```{r}
SOFAdata <- 
  read_excel(datafile, na='NULL', sheet = 'SOFA', range = 'A1:BX1609') %>% 
  select(c(PersonalID,
          SOFATotalPoint,
          KDIGOMin,
          #vaso
          Dopamin,
          Adrenalin,
          Noradrenalin,
          Dobutamin,
          Levosimendan,
          Vasopressin,
          DaysWithVasopressorsInotropes)) %>% 
  mutate(KDIGOMin = as.character(KDIGOMin))


```


## measures sheet - select and calculate variables
```{r}
measuresdata <- 
  read_excel(datafile, na='NULL', sheet = 'Measures', range = 'A1:BC1609') %>%
  select(c(PersonalID,
          `DG021 min`,
          `DG021 days`,
          `DG023 min`,
          `DG028 min`,
          `SR320 min`,
          `DV023 days`,
          `DR020 min`)) %>% 
  mutate(
    # ventilation
    InvasiveMechanicalVentilation = `DG021 min` > 0,
    InvasiveMechVentDays = if_else(`DG021 days`==0,
                                  as.numeric(NA), `DG021 days`),
    NonInvasiveMechVent = `DG023 min` > 0,
    OxHighFlowNasalCanula = `DG028 min` > 0,
    CarePronePatient = `SR320 min` > 0,
    ECMO = `DV023 days` >0,
    CRRT = `DR020 min` > 0
  )

```


## SIRI sheet - select and calculate variables
```{r}
SIRIdata <- 
  read_excel(datafile, na='NULL', sheet = 'SIRI', range = 'A1:AZ1609') %>% 
  select(c(PersonalID,
          # specific
          CovidMedicineKlorokinfosfat,
          CovidMedicineLopinavir,
          CovidMedicineLopinavirRitonavir,
          CovidMedicineRemdesivir,
          CovidMedicineTocilizumab,
          CovidMedeicineSteroids,
          #other
          CovidMedicineDarunavir,
          CovidMedicineVitamineC,
          CovidMedicineOther,
          # comorbidities
          RiskHypertension,
          RiskChronicHeartDisease,
          RiskChronicLungDisease,
          RiskObesity,
          RiskDiabetes,
          RiskChronKidneyDisease,
          RiskChronicLiverDisease,
          RiskNeuroMuscDisease,
          RiskReducedImmuneDefence,
          DaysToICUFromIllness)) %>% 
  mutate(
    # convert to logical
    across(starts_with('CovidMedicine') | starts_with('Risk'), as.logical),
    
    # replace negative with NA
    DaysToICUFromIllness = if_else(DaysToICUFromIllness < 0, 
                              as.numeric(NA), 
                              DaysToICUFromIllness),
    DaysToICUIllnessCategory = case_when(DaysToICUFromIllness < 4 ~ '<4',
                                         between(DaysToICUFromIllness,4,7) ~ '4-7',
                                         DaysToICUFromIllness >= 8 ~ '8+'),
    
    # either of these
    LopinavirOrRitonavir = pmax(CovidMedicineLopinavir,
                          CovidMedicineLopinavirRitonavir,
                          na.rm = TRUE) %>% as.logical())


```

# calculate obesity data
```{r}
basicdata <- basicdata %>% 
  full_join(SIRIdata %>% select(PersonalID,RiskObesity)) %>% 
  mutate(RiskObesity40 = coalesce(BMI40plus, RiskObesity))

```

# create variables with any "1" in a list of other variables
```{r}

# "Any" of a list variables

comorbiddata <- SIRIdata %>% 
  select(c(PersonalID,
           RiskHypertension,
           RiskChronicHeartDisease,
           RiskChronicLungDisease,
           RiskDiabetes,
           RiskChronKidneyDisease,
           RiskChronicLiverDisease,
           RiskNeuroMuscDisease,
           RiskReducedImmuneDefence)) %>% 
  full_join(basicdata %>% select(c(PersonalID, RiskObesity40))) %>% 
      pivot_longer(cols = -c(PersonalID),
                   names_to = c('Comorbidity')) %>% 
      group_by(PersonalID) %>%
      summarise(ComorbidityAny = ifelse(all(is.na(value)),
                                        NA, sum(value, na.rm = TRUE)
                                        ) %>% sign() %>% as.logical()
                )

specpharmdata <- SIRIdata %>% 
  select(c(PersonalID,
           CovidMedicineKlorokinfosfat,
           CovidMedicineLopinavir,
           CovidMedicineLopinavirRitonavir,
           CovidMedicineRemdesivir,
           CovidMedicineTocilizumab,
           CovidMedeicineSteroids)) %>% 
      pivot_longer(cols = -c(PersonalID),
                   names_to = c('SpecificPharmacotherapy')) %>% 
      group_by(PersonalID) %>%
    summarise(SpecPharmAny = ifelse(all(is.na(value)), 
                              NA, sum(value, na.rm = TRUE)
                              ) %>% sign() %>% as.logical()
    )
  
otherpharmdata <- SIRIdata %>% 
  select(c(PersonalID,
           CovidMedicineDarunavir,
           CovidMedicineVitamineC,
           CovidMedicineOther)) %>%
  pivot_longer(cols = -c(PersonalID),
               names_to = c('OtherPharmacotherapy')) %>%
  group_by(PersonalID) %>%
  summarise(OtherPharmAny = ifelse(all(is.na(value)),
                                NA, sum(value, na.rm = TRUE)
                                ) %>% sign() %>% as.logical()
    )

vasodata <- SOFAdata %>%
  select(c(PersonalID,
           Dopamin,
           Adrenalin,
           Noradrenalin,
           Dobutamin,
           Levosimendan,
           Vasopressin)) %>%
  pivot_longer(cols = -c(PersonalID),
               names_to = c('VasopressorsInotropes')) %>% 
  mutate(valueBinary = case_when(value == 'No' ~ 0,
                                 (is.na(value) | value=='Missing') ~ as.numeric(NA),
                                 value != 'No' ~ 1
                                 )) %>%
  group_by(PersonalID) %>% 
  summarise(VasoInoAny = ifelse(all(is.na(valueBinary)), 
                              NA, sum(valueBinary, na.rm = TRUE)
                              ) %>% sign() %>% as.logical()
            )

```

# make the analysis dataset
```{r}

# join datasets by PersonalID
swecovdata <- comorbiddata %>% 
  full_join(specpharmdata) %>% 
  full_join(otherpharmdata) %>% 
  full_join(vasodata) %>% 
  full_join(basicdata) %>% 
  full_join(measuresdata) %>% 
  full_join(SOFAdata) %>% 
  full_join(SIRIdata) %>%
  full_join(diagnosisdata) %>% 
  # remove variables that were used for calculation and no longer needed
  select(-c(PersonalID,
            Deceased,
            ArrivalBMI,
            BMI40plus,
            RiskObesity,
            NumberOfICUTransfers,
            SAPS3TimeInHospital,
            J809X,
            J809A,
            J809B,
            J809C,
            `DG021 min`,
            `DG023 min`,
            `DG028 min`,
            `SR320 min`,
            `DV023 days`,
            `DR020 min`,
            CovidMedicineLopinavir,
            CovidMedicineLopinavirRitonavir,
            OffRegistryDate,
            AdmissionRegistration,
            DaysDischargeOffReg,
            Dopamin,
            Adrenalin,
            Noradrenalin,
            Dobutamin,
            Levosimendan,
            Vasopressin
         )) %>%
  filter(!is.na(Mortality30days))

write_csv(swecovdata,'../SweCovICU_AnalysedData.csv')

# swecovdata %>%
#   filter(Mortality30days & is.na(DaysToDeath)) %>% 
#   pull(PersonalID)

# swecovdata %>% 
#   filter(`DaysFromDischargeToOff-registry/Diseased` < 0)
# 
# swecovdata %>% 
#   tabyl(BMIover30) %>% 
#   adorn_totals() %>% 
#   adorn_pct_formatting()
# 
# swecovdata %>%
#   group_by(is.na(ArrivalBMI), RiskObesity) %>%
#   tally()
# 
# swecovdata %>%
#   filter(ArrivalBMI >=40 & RiskObesity == 0) %>% 
#   pull(ArrivalBMI)
# 
# swecovdata %>%
#   filter(ArrivalBMI <40 & RiskObesity == 1) %>% 
#   summarise(minBMI = min(ArrivalBMI),
#             maxBMI = max(ArrivalBMI))
# 
# swecovdata %>% 
#   group_by(BMI40plus, RiskObesity) %>% 
#   tally()
# 
# obesityplot <- swecovdata %>% 
#   mutate(ArrivalBMI = ArrivalBMI %>% parse_number(),
#          RiskObesity = RiskObesity %>% as.logical()) %>% 
#   ggplot(aes(x = ArrivalBMI, fill = RiskObesity)) +
#   facet_wrap(~RiskObesity, scales = 'free', ncol = 1) +
#   geom_histogram(binwidth = 5, colour = 'black') + 
#   coord_cartesian(xlim = c(0,80)) +
#   theme_bw()


```

# Summary table

```{r echo=FALSE}
dfSummary(swecovdata) %>% view()
```


